Bearing Fault Diagnosis Based on Deep Belief Network

### 2019-06-12 Paper/main.tex
no message

\subsection{Back Propagation and DBN}
First we compare the differences between DBN and traditional back propagation neural network. As we can see from Fig. \ref{fig:dbnVSbp}, there was no significant improvement in the accuracy rate of the back propagation neural network in the first 200 epoches. The accuracy rate is about the accuracy rate at random selection, i.e. 10\%.

@@

\subsection{Sigmoid and Isigmoid}
Isigmoid proposed by Yi Qin \cite{YiThe} is capable to relax the vanishing gradient problem and converges faster then Sigmoid. As shown in Fig. \ref{fig:SigmoidVSIsigmoid}, since we did not use Isigmoid in RBM (pre-training), their initial accuracy rates are similar. However, when using Isigmoid in the back propagation, the DBN can converge faster and has higher accuracy rate.

@@

\subsection{DBN and SSDBN}
\textcolor{red}{Finally, we compare DBN with SSDBN. Since SSDBN has studied the sample labels at RBM, I thought that the initial classification accuracy rate should be higher than DBN, but the result is not the case. And DBN seems to converge faseter than SSDBN. However, the final classification accuracy rate of SSDBN is higher than DBN.}

@@

>>>>

\subsection{DBN}
First we compare the differences between DBN and traditional back propagation neural network. As we can see from Fig. \ref{fig:dbnVSbp}, there was no significant improvement in the accuracy rate of the back propagation neural network in the first 200 epoches. The accuracy rate is about the accuracy rate at random selection, i.e. 10\%.

@@

\subsection{Isigmoid}
Isigmoid proposed by Yi Qin \cite{YiThe} is capable to relax the vanishing gradient problem and converges faster then Sigmoid. As shown in Fig. \ref{fig:SigmoidVSIsigmoid}, since we did not use Isigmoid in RBM (pre-training), their initial accuracy rates are similar. However, when using Isigmoid in the back propagation, the DBN can converge faster and has higher accuracy rate.

@@

\subsection{SSDBN}
\textcolor{red}{Next we compare DBN with SSDBN. Since SSDBN has studied the sample labels at RBM, I thought that the initial classification accuracy rate should be higher than DBN, but the result is not the case. And DBN seems to converge faseter than SSDBN. However, the final classification accuracy rate of SSDBN is higher than DBN.}

@@

Fig. \ref{fig:SSDBNIsigmoid} shows that by combining SSDBN with Isigmoid, we can further improve the classification accuracy.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth]{SSDBNIsigmoid.eps}
	\caption{Comparison of classification accuracy between SSDBN using Sigmoid and SSDBN using Isigmoid in 1000 epoches.}
	\label{fig:SSDBNIsigmoid}
\end{figure}

In the traditional back propagation neural network, the accuracy rate of the training dataset is 97.12\%, and the accuracy rate of the testing dataset is 95.83\%. In the SSDBN using Isigmoid, the accuracy rate of the training dataset is 98.87\%, and the accuracy rate of the testing dataset is 97.33\%.
